### 2025-04-16 Manuscript/Manuscript.tex
writting

In this conditions we know the known as \gls{srm} \footnote{a.k.a. pretty good measurement.} to be optimal, i.e. the result of the \gls{sdp} is the same as the \gls{srm}. This measurement is the one obtained by the decomposition of the Gram matrix the square root of an hermitian matrix $S$ as the following,
\begin{align*}
	\mathcal{G}=S^\dagger S=S^2.
\end{align*}
this measurement is the estandard in \gls{qsd} for the \gls{me} protocol \cite{OptimalitySRM}.

@@

Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one. Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol. Hence, the probabilities for

>>>>

In this conditions we know the known as \gls{srm} \footnote{Also known as \emph{pretty good measurement}.} to be optimal, i.e. the result of the \gls{sdp} is the same as the \gls{srm}. This measurement is the one obtained by the decomposition of the Gram matrix the square root of an hermitian matrix $S$ as the following,
\begin{align*}
	\mathcal{G}=S^\dagger S=S^2.
\end{align*}
this measurement is the estandard in \gls{qsd} for the \gls{me} protocol \cite{OptimalitySRM}.

@@

Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one. Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol. Hence, the success probabilities for \gls{me} are greater than the ones obtained with the \gls{ze} protocol.

We compare both protocols as well as the outcome of the \gls{srm} in Figure (\ref{FigureQSDMEZESRM}).

\begin{figure}[H]
	\centering
	\label{FigureQSDMEZESRM}
	\includegraphics[width=0.5\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Zero Error (\gls{ze}) Minimum Error (\gls{me}) protocols and the Square Root Measurement (\gls{srm}).}
\end{figure}

We observe perfect discrimination in not possible unless we impose orthogonality (i.e. overlap $= 0$), the trivial ensemble. This result is the main difference between the discrimination and exclusion task and the main motivation in the reserch on quantum state exclusion \gls{qse}.

In contrast, in Figure (\ref{FigureQSEMEZ3ZHeatmap}) we present the results for the Quantum State Exclusion (\gls{qse}) for the $\mathbb{Z}/3\mathbb{Z}$ for the \gls{me} protocol in an analogously to Figure (\ref{FigureQSDMEZ3ZHeatmap}).

\begin{figure}[H]
	\centering
	\label{FigureQSEMEZ3ZHeatmap}
	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
		\put(60,25){$G<0$}
		\put(60,55){$G<0$}
	\end{overpic}
	\caption{Representation of the probability of successfull exclusion for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Minimum Error (\gls{me}) protocol.}
\end{figure}

We observe perfect exclussion can be performed in esembles such that perfect discrimination is not possible, particularly ensembles that fulfil Eq. (\ref{equationPerfectExclusionCondition}). This regime is highlighted in Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}), where both regimes are clearly distinguished.

\begin{figure}[H]
	\centering
	\label{FigureQSEMEZ3ZPerfectExclusion}
	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
		\put(60,25){$G<0$}
		\put(60,60){$G<0$}
	\end{overpic}
	\caption{Representation of the perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Minimum Error (\gls{me}) protocol.}
\end{figure}
